Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-08-15 manuscript/Chapter3-manuscript.Rmd
update sentence in intro

There currently is a lack of consensus on whether specializing or flexible foraging is best in nature along with the ecological contexts favoring one strategy over the other. Studies investigating the fitness benefits of specialization show contrasting results; some report increasing benefits of specializing [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015]. ici, essayer de poser la question de genre cela nous fait se demander pourquoi se spécialiser?? um peu comme woo a fait. ça va lier au fait ensuite que je parle des proies

>>>>

There currently is a lack of consensus on the fitness consequences of specializing vs flexible foraging along with the ecological contexts favoring one strategy over the other. Studies investigating the benefits of specialization show contrasting results; some report increasing benefits of specializing [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015]. ici, essayer de poser la question de genre cela nous fait se demander pourquoi se spécialiser?? um peu comme woo a fait. ça va lier au fait ensuite que je parle des proies
